---
title: "NETFLIX"
author: "Maxwell_teye_kpakpaku"
date: "2024-03-30"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NETFLIX

Netflix is the leading online movie channel found in 1997. Netflix was founded by Marc Randolph and Reed Hastings. Initially, Netflix offered a per-rental model for each DVD but introduced a monthly subscription concept in September 1999. On October 1, 2006, Netflix announced the Netflix Prize, \$1,000,000 to the first developer of a video-recommendation algorithm that could beat its existing algorithm Cinematch, at predicting customer ratings by more than 10%. On September 21, 2009, it awarded the \$1,000,000 prize to team "BellKor's Pragmatic Chaos". Cinematch, launched in 2000, is a recommendation system that recommended movies to its users, many of which they might not ever had heard of before.

### objectives

data transformation

Exploratory Data Analysis.

## load dataset

```{r}
library(dplyr)
library(tidyverse)
library(plotly)
library(tinytex)
library(rmarkdown)
library(tidytext)
library(treemap)
library(ggplot2)
```

```{r data}
data = read_csv("/Users/Maxwell/Desktop/DATASET FOR PRACTICE/netflix1.csv")
str(data)
```

```{r data}
data
```

## data cleaning

```{r data}
data1 = data%>%
  drop_na()%>%
  distinct()
```

```{r data1}
ggplot(data1, mapping = aes(type, ))+
  geom_bar(fill = "skyblue")+
  labs(title = "The count of the movie type", x = "type", y = "count of the types")
```

```{r data1}
datacount = data1%>%
  group_by(release_year)%>%
  summarise(count = n())
```

### count of movies in a year

```{r data1}
p = ggplot(datacount, mapping = aes(x= release_year, count))+
  geom_line(colour = "red", size = 1)+
  geom_point()+
  labs(title = "Count of Dates", x = "Date", y = "Count")+
  theme_minimal()

gg_plot = ggplotly(p)
gg_plot
  
```

## Rank top 10 movie producing countries

```{r}
country_count = data1 %>%
  group_by(country)%>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  slice(1:10)
ggplot(country_count, mapping = aes( count, reorder( country, count) , fill = country) )+
  geom_bar(stat = "identity")+
  labs(title = "The top 10 movie making countries", x = "Country", y = " Total of number movies made")
```

## Ranking of top 20 movie categories

```{r}
tokenized = data1%>%
  unnest_tokens(phrase, listed_in, token = "regex", pattern = "[,&]")%>%
  mutate(phrase = str_trim(phrase))

##tokenize the movies genre
word_count = tokenized%>%
  group_by(phrase)%>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  slice(1:20)
## plot of ranking barchart
plot = ggplot(word_count, mapping = aes(x= count, y= reorder( phrase,count), fill = phrase))+
  geom_bar(stat = "identity")+
  labs(title = "Rank of the top 20 movie categories", x= "Count on movies", y = "Category of Movie")


pltly = ggplotly(plot) 

pltly



```

## Comparing months

```{r}
month = data1%>%
  mutate(date_added = as.Date(date_added, format = "%m/%d/%Y"))%>%
  mutate(month = month(date_added))%>%
  group_by(month)%>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  mutate(monthname = month.name[month])


month

treemap = ggplot(month, aes(area = count, fill = monthname))+
  geom_treemap()+
  geom_treemap_text(aes(label = monthname), place = "centre")+
  labs(title = "TREEMAP")+
  theme_minimal()

```

### List of directors and number of movies directors

```{r}
directors = data1%>%
  group_by(director)%>%
  summarise(count = n())%>%
  arrange(desc(count))%>%
  filter(director != "Not Given")

directors


```

### list of movies in seasons

```{r}
time_spent = data1%>%
  filter(str_detect(duration, "Season"))%>%
  separate(duration, into = c("number of seasons", "season"), sep = " ")

group_time_spent = time_spent%>%
  group_by(`number of seasons`)%>%
  summarise(            count = n())%>%
  arrange(desc(count))
group_time_spent
```

### lenght of movies in minutes

```{r}
minutes = data1%>%
  filter(str_detect(duration, "min"))%>%
  separate(duration, into = c("number of minutes", "mins"), sep = " ")

group_min = minutes%>%
  group_by(`number of minutes`)%>%
  summarise(count = n())%>%
  arrange(desc(as.integer(`number of minutes`)))
group_min
```
